Analyzing opportunities arround city traffic optimization

### 2020-01-19 thesis/report1.tex
Referral 1: added a figure and some words on analyzers.

\documentclass[a4paper,12pt,twoside]{book}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{apacite}
\usepackage{natbib}
\usepackage{listings}

@@

@@

@@

>>>>

\documentclass[a4paper,12pt,twoside]{book}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{apacite}
\usepackage{natbib}
\usepackage{listings}
\usepackage{graphicx}

@@

\begin{figure*}
    \includegraphics[width=0.9\linewidth]{ScreenshotWebInterface2.jpg}
    \centering
    \caption{Screenshot of the web interface showing the running simulation}
    \label{fig:ScreenshotWebInterface2}
  \end{figure*}

@@

The central piece of those analyzers is the city simulator. It contains all the centralized data, from all its actors and it has a minimal API (Application Programming Interface) to serve this data. Actors are the first to consume it as they might need various pieces of information to wisely choose their track. A separate microservice may be the one which takes this data and analyzes it further. The reason for a separate microservice is the separation of concerns. The city simulator is responsible only for keeping together the data and serving it. Any other duty of transform, extrapolate, etc. is not its task to do.

Therefore few ways of taking advantage of this data are described below. They are by no means exhaustive and represent only few places to start.

@@

Hot areas are defined as places or streets where traffic is pilling up more than in other areas. Intuitively
